List of Items

### 2020-04-23 manuscript.RmD
- update website

  This manuscript features online supplementary material that includes the code, additional analyses, and a reproducible version of the manuscript (https://osf.io/4wabh). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level). 
  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  Together, the results provide further evidence against the privacy paradox.
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [bibliography/references.bib]
  - [bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines; comment lines after "output: html_document ..."
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

@@

For the analyses, coding, and typesetting, we used `r r_citations`.
The code, additional analyses, and a reproducible version of this manuscript can be accessed in the Online Supplementary Material (OSM) at https://osf.io/4wabh.

>>>>

  This manuscript features a companion website that includes detailed summaries of the statistical results, the code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy-paradox-longitudinal). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level). 
  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  Together, the results provide further evidence against the privacy paradox.
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [bibliography/references.bib]
  - [bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines; comment lines after "output: html_document ..."
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

@@

For the analyses, coding, and typesetting, we used `r r_citations`.
The code, additional analyses, and a reproducible version of this manuscript can be found on the manuscript's companion website at https://tdienlin.github.io/privacy-paradox-longitudinal.
